### 2019-03-12 paper/sex_selection_spacing-ver2.tex
Minor edits

For legibility none of the graphs show standard errors.
Instead, the standard errors, together with the graphed values, are shown in Appendix 
Tables TK, TK, and TK.%
\footnote{
Furthermore, Appendix Tables \ref{tab:p25_p75_low}, \ref{tab:p25_p75_med}, and 
\ref{tab:p25_p75_high} show 25th, 50th, and 75th percentiles durations with
bootstrapped standard errors.
} 
The standard errors are based on bootstrapping for all three measures,
where the model is repeatedly estimated using resampling with replacement.

@@

Women with eight or more year of education mostly followed 
the traditional spacing pattern before sex selection became 
available as shown in Table \ref{tab:median_sex_ratio_high}.
Compared to the two other education groups there are,
however, more situations where the pattern is less clear.
Part of the problem may be that there are few women in
this group for the 1972--1984 period, and, hence, only 
the results for the first and second spells in both urban 
and rural areas are likely reliable.

@@

\subsection{Distribution of Birth Spacing Across Sex Compositions and Time}

Median spacing is a convenient way to understand the overall changes but
may hide important differences in the distribution of spacing.
This section, therefore, provides more detail on how spacing is distributed
over time and sex compositions using a graphical approach.

>>>>

For legibility none of the graphs show standard errors.
Instead, the standard errors, together with the graphed values, are shown in Appendix 
Tables TK, TK, and TK.
The standard errors are based on bootstrapping for all three measures,
where the model is repeatedly estimated using resampling with replacement.

@@

Women with eight or more year of education mostly followed 
the traditional spacing pattern before sex selection became 
available as shown in Figure \ref{fig:bootstrap_high}.
Compared to the two other education groups there are,
however, more situations where the pattern is less clear.
Part of the problem may be that there are few women in
this group for the 1972--1984 period, and, hence, only 
the results for the first and second spells in both urban 
and rural areas are likely reliable.

@@

\subsection{How the Distribution of Birth Spacing Varies Across Sex Compositions and Time}

Median spacing is a convenient way to understand the overall changes but
may hide important differences in the distribution of spacing.
This section, therefore, provides more detail on how spacing is distributed
over time and sex compositions using a graphical approach.%
\footnote{
Furthermore, Appendix Tables \ref{tab:p25_p75_low}, \ref{tab:p25_p75_med}, and 
\ref{tab:p25_p75_high} show 25th, 50th, and 75th percentiles durations with
bootstrapped standard errors.
}
